Tidy Data

### 2014-01-08 reviews/response.md

> Section 2: "When using tables for communication, this so-called 
> "Alabama first" (Wainer 2000) ordering should be abandoned, and replaced 
> with an ordering based on a meaningful variable."
> 
> There doesn't seem to be any justification or explanation for this statement.
> (R3)

Removed.

> Section 3.1: Since most readers of this paper will want to apply these ideas 
> using R, I think it would be a good idea to show how an R datasets containing 
> the Pew and Billboard data would look, as well as the R code that would be 
> used to melt the datasets. This is especially true for the Billboard data, 
> because additional cleaning was performed. Similar comments apply to the 
> other datasets in the paper. (R3)

I think including the code in the paper would make it too long, but they
are all available at the paper website at https://github.com/hadley/tidy-data

@@

> Section 3.5: I feel the examples in this section need to be explained in 
> more detail. The referenced external links contain a large number of files, 
> and it's not really clear which files are relevant to the discussion in this 
> section. (R3)

I've added a brief snippet of R code to illustrate how you might tackle this.

@@

> Section 4.1: "Compare this to the difficulty of combining datasets stored in 
> arrays; these typically require painstaking alignment before matrix 
> operations can be used, and errors can be very hard to detect."
> Would anyone seriously suggest using matrices to store data which would be 
> combined with other data sets? The use of an index to combine multiple 
> datasets doesn't really seem to be related to tidy data. (R3)

Right, and I've now removed this sentence.

> Section 5: I was not able to download the data for the case study from 
> https://raw.github.com/hadley/tidy-data/master/case-study/deaths.rdata; 
> I recieved a 403 Forbidden error. (R3)

Smaller version that you can download now at 
https://raw.github.com/hadley/tidy-data/master/case-study/deaths.rds

### 2014-01-08 tidy-data.tex
Minor problems from reviewer 3

>>>>

The \pkg{plyr} package makes this straightforward in \proglang{R}. The following code generates a vector of file names in a directory (\code{data/}), matching a regular exrepssion (ends in \code{.csv}). Next we name each element of the vector with the name of the file. We do this because \pkg{plyr} will preserve the names in the next step, ensuring that each row in the final data frame is labelled with its source. Finally, \code{ldply()} loops over each path, reading in the csv file and combining the results into a single data frame.

\begin{Verbatim}
paths <- dir("data", pattern = "\\.csv$", full.names = TRUE)
names(paths) <- basename(paths)
ldply(paths, read.csv, stringsAsFactors = FALSE)
\end{Verbatim}
